Exploratory analysis of context: Regression Analysis

### 2021-11-29 analysis/exploratory/context_versus_nocontext/rscripts/analysis.Rmd
updated talk for linguae

```{r}
# Make everything into a factor
d$Wh = as.factor(d$Wh)
d$workerid = as.factor(d$workerid)
d$tgrep_id = as.factor(d$tgrep_id)
d$paraphrase = as.factor(d$paraphrase)
d$ModalPresent = as.factor(d$ModalPresent)
d$Task = as.factor(d$Task)
```
# Does cTask predict rating?

@@

# m.ms.ma.full = lmer(normed_rating ~ cParaphrase*Wh*cModalPresent*cTask + (1+cParaphrase+Wh+cModalPresent|workerid) + (1+cParaphrase+cTask|tgrep_id), data=d.ms.ma)

>>>>

```{r}
# Make everything into a factor
d$Wh = as.factor(d$Wh)
d$workerid = as.factor(d$workerid)
d$tgrep_id = as.factor(d$tgrep_id)
d$paraphrase = as.factor(d$paraphrase)
d$ModalPresent = as.factor(d$ModalPresent)
d$Task = as.factor(d$Task)
```
# Does cTask predict rating?
- Yes, and there's an interaction

@@

# m.ms.ma.full = lmer(normed_rating ~ cParaphrase*cTask + (1+cParaphrase|workerid) + (1+cParaphrase+cTask|tgrep_id), data=d.ms.ma)
# saveRDS(m.ms.ma.full, "../models/model-task-para.rds")

m.ms.ma.full <- readRDS("../models/model-task-para.rds")
summary(m.ms.ma.full)
